Double-Drift Illusion Boundaries

### 2020-05-28 DoubleDriftResetLimits.Rmd
added time-model exploration plot

We've minimized depencies on other packages, but there are two that help. Of course, you can skip the chunks that use them, or just install them by uncommenting the second line of this chunk:

@@

```{r}
# The functions here allow downloading the collected data from the OSF project:
source('R/data.R')
# This file has some common helper functions:
source('R/common.R')
# The functions in here are used on the data of the bounded tracking experiments:
source('R/tracking_bounded.R')
# And finally some code for the re-tracing experiment...
source('R/retrace_onePass_V4.R')
# As well as models fit to that data:
source('R/models.R')
```

@@

In order to determine the point of reset automatically, we took the first sign change of the X coordinate. Since the start of the tracing often was somewhat "shaky" we disregarded sign changes in the first XXX cm. Since the trajectories are measured in discrete pixel values, sign changes were clearer after slight smoothing of the trajectories, using splines.

@@

>>>>

We've minimized depencies on other packages, but there are three that help. Of course, you can skip the chunks that use them, or just install them by uncommenting the second line of this chunk:

@@

```{r}
# The functions here allow downloading the collected data from the OSF project:
source('R/data.R')
# This file has some common helper functions:
source('R/common.R')
# The functions in here are used on the data of the bounded tracking experiments:
source('R/tracking_bounded.R')
# And finally some code for the re-tracing experiment...
source('R/retrace_onePass_V4.R')
# As well as models fit to that data:
source('R/models.R')
# Comparison with Sirui Liu's data:
source('R/time.R')
```

@@

In order to determine the point of reset automatically, we took the first sign change of the X coordinate. Since the start of the tracing often was somewhat "shaky" we disregarded sign changes in the first 75 px or XXXX cm. Since the trajectories are measured in discrete pixel values, sign changes were clearer after slight smoothing of the trajectories, using splines.

```{r}
retrace <- read.csv('data/onePass_V4/onePass_V4_re-trace.csv', stringsAsFactors = F)
retrace$value <- 1
retrace$value[which(is.na(retrace$boundX))] <- 0
resetcounts <- aggregate(value ~ participant, data=retrace, FUN=sum)
resetcounts$value <- resetcounts$value / (6*6*4)
print(resetcounts)
```

We can also look at this, further split by condition:

```{r}
resetcountsCOND <- aggregate(value ~ participant + internalspeed + externalspeed, data=retrace, FUN=sum)
print(resetcountsCOND)
hist(resetcountsCOND$value)
```

This distribution appears to be bimodal. Since resets here depend on direction inversion, and some people may experience more "hit-the-wall resets", it seems that the lower peak could be from people with hit-the-wall resets, while the other participants perceive some return to the true position.

@@

# Alternative Time Model

This model is based on the work by Sirui Liu and colleagues who found that when probing the location of the stimulus at a few fixed temporal offsets from stimulus onset it deviated less and less after more time. This is consistent with a simple model with a fixed, fairly low chance of a reset occurring at every time point. That is: as time goes by the likelihood of reset having occurred is larger, and as a result the average percept is closer to the true position over time. This model fits very well and is completely at odds with the findings here. So which is true?

One way both may be true at the same time, is if after a reset, the illusion builds up less or not at all. In the current experiment people report the full path of the stimulus, so we can also look at the average deviation of the perceived position from the true position over time, continuously. This allows to see if it is in line with the data reported by Liu, Tse & Cavanagh [].
